\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\noindent
\textbf{Rajan Saha Raju,Reg\# 2015331010} \newline
Technical Writing \newline
Article Review, 27 September 2018 \newline \\

\begin{flushright}
\textbf{Bringing IoT and Cloud Computing towards Pervasive Healthcare} \newline 
\textbf{Charalampos Doukas and Ilias Maglogiannis}
\end{flushright}

\begin{flushleft}
\justify
Doukas, Charalampos, and Ilias Maglogiannis. "Bringing IoT and cloud computing towards pervasive healthcare." Innovative Mobile and Internet Services in Ubiquitous Computing (IMIS), 2012 Sixth International Conference on. IEEE, 2012.\newline \\
\end{flushleft}

\justify
\hspace{1cm}A Healthcare System has been proposed that will capable of receiving patient’s medical condition (pulse rate,blood pressure,breath alcohol level and so on) from Wearable Sensors,mobile devices,Internet of Things(IoT) and forwarding data to managing application running in Cloud and then passing to health caregivers for analysis.

\justify
\hspace{1cm}It’s an amusing proposal in the arena of medical science.The aim of the proposed system is efficient management of cloud computing , IoT and providing medical service to independent living of elderly people,chronic patients or habitants at underserved locations.

\justify
\hspace{1cm}Since this Cloud computing and IoT based system deals with the patient medical data,main challenge is the security of privacy of data. Another issues that can be traced is energy efficiency of Wearable sensors and microcontroller embedded in IoT.

\justify
\hspace{1cm}Initial experiment has detected some bugs like drop packet of data due to network congestion or transmitting data at a same time.For betterment a solution has been deployed.Author claim as managing application is basis on Cloud computing infrastructure and share common resource,it will be an outstanding solution for efficient management of healthcare data.

\justify
\hspace{1cm}The paper is enough clear and reader can easily understand what author wants to express.Figure described in the paper visualizes the whole system more comprehensively.But there is no statistical analysis of how smoothly system works with the increasing number of users. Most of the references used here are recent.

\newpage


\justify
\hspace{1cm}If the system can be implemented,it will open a new horizon in medical science.
\end{document}
